Joint maximum-likelihood of phylogenies and ancestral states is not consistent

### 2018-06-26 appendix.tex
updated plots... looks like we found it! time to triple check...

$\{2,3\}$  &$\emptyset$&$(1+x_1)(1-y_1)(1-x_2)(1+y_2)(1+w)$\\
&$\{1\}$&$(1-x_1)(1-y_1)(1+x_2)(1+y_2)(1-w)$\\
&$\{1,2\}$&$(1-x_1)(1+y_1)(1+x_2)(1-y_2)(1+w)$\\
\hline
\end{tabular}
\caption{
Due to the symmetry of the likelihood, WLOG we assume $x_2 > x_1$ and $y_2 > y_1$ and maximize over ancestral states to reduce the number of possible functional forms to consider.
All values multiplied by $1/32$.
Likelihoods with multiple entries have maxima determined by unknown branch length parameters.
See Table~\ref{tab:farris_likelihoods} for full calculations.}
\label{tab:likelihoods}
\end{table}
%TODO: the caption of this overlaps with the page number---will this be a problem or will MBE handle it?
%EM There is a latex package for that, which I tried out and then removed for some reason. It's no bigs.

@@

\begin{figure}
\centering
%python joint_inf_plot.py --analytic --plot-name svg-fig/positive-gradients.svg --delta .001
\includegraphics[width=.95\textwidth]{positive-gradients}
\caption{
}
\label{fig:positive-gradients}
\end{figure}

@@

\begin{figure}
\centering
%python joint_inf_plot.py --empirical --plot-name svg-fig/empirical-incons-curve.svg --delta .01 --n-jobs 10 --plot-curve
\includegraphics[width=.95\textwidth]{empirical-incons-curve}
\caption{
Inconsistency in joint inference with intuitive curves.
The white curve is our condition on the gradients.
The blue curve is a condition on $x^*$ and $y^*$ such that $\emptyset$ is the most likely ancestral state.
}
\label{fig:empirical-incons}
\end{figure}

>>>>

$\{2,3\}$  &$\emptyset$&$(1+x_1)(1-y_1)(1-x_2)(1+y_2)(1+w)$\\
&$\{1\}$&$(1-x_1)(1-y_1)(1+x_2)(1+y_2)(1-w)$\\
&$\{1,2\}$&$(1-x_1)(1+y_1)(1+x_2)(1-y_2)(1+w)$\\
\hline
\end{tabular}
\caption{
Due to the symmetry of the likelihood, WLOG we assume $x_2 \ge x_1$ and $y_2 \ge y_1$ and maximize over ancestral states to reduce the number of possible functional forms to consider.
All values multiplied by $1/32$.
Likelihoods with multiple entries have maxima determined by unknown branch length parameters.
See Table~\ref{tab:farris_likelihoods} for full calculations.}
\label{tab:likelihoods}
\end{table}
%TODO: the caption of this overlaps with the page number---will this be a problem or will MBE handle it?
%EM There is a latex package for that, which I tried out and then removed for some reason. It's no bigs.

@@

\begin{figure}
\centering
%python joint_inf_plot.py --optimum-conditions --plot-name svg-fig/positive-gradients.svg --delta .001 --n-jobs 10
\includegraphics[width=.95\textwidth]{positive-gradients}
\caption{
}
\label{fig:positive-gradients}
\end{figure}

\begin{figure}
\centering
%python joint_inf_plot.py --analytic --plot-name svg-fig/incons-analytic.svg --delta .001 --n-jobs 10
\includegraphics[width=.95\textwidth]{incons-analytic}
\caption{
Region of inconsistency.
}
\label{fig:incons-analytic}
\end{figure}

@@

\begin{figure}
\centering
%python joint_inf_plot.py --empirical --plot-name svg-fig/empirical-incons-intuition.svg --delta .01 --n-jobs 10 --plot-intuition
\includegraphics[width=.95\textwidth]{empirical-incons-intuition}
\caption{
Inconsistency in joint inference with intuitive curves.
The white curve is our condition on the gradients.
The blue curve is a condition on $x^*$ and $y^*$ such that $\emptyset$ is the most likely ancestral state.
}
\label{fig:empirical-incons-intuition}
\end{figure}

\begin{figure}
\centering
%python joint_inf_plot.py --empirical --plot-name svg-fig/empirical-incons-analytic.svg --delta .01 --n-jobs 10 --plot-curve
\includegraphics[width=.95\textwidth]{empirical-incons-analytic}
\caption{
Inconsistency in joint inference with bounding curve.
}
\label{fig:empirical-incons-analytic}
\end{figure}
